---
title: "73rd Annual Golden Globes Twitter Analysis"
author: Boying Gong, Jianglong Huang, Peter Sujan, Shamindra Shrotriya, Tomofumi Ogawa
date: February 8, 2016
output: beamer_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r, echo=FALSE, cache=TRUE}
source("./read_data.R")
head(combined_timelines)
```

## Slide with Plot

```{r, echo=FALSE}
tail(combined_timelines)
```


```{r, echo=FALSE}
head(combined_timelines)
```

## Jianglong Slide 1

```{r,echo=FALSE,message=FALSE}
source("./JH_function.R")
combined_timelines=JH_dataframe_addcolumn(combined_timelines)
agg.heat=JH_heatmap_df_generation(combined_timelines)
JH_heatmap_plot(agg.heat)
```

## Jianglong Slide 2

```{r,echo=FALSE,message=FALSE}
people=JH_tweet_power_df_generation(combined_timelines,nominees_metadata)
JH_tweet_power_scatter_plot(people)
```

## Jianglong Slide 3

```{r,echo=FALSE,message=FALSE}
JH_tweet_power_profile_plot(people)
```

## Peter Slide 1
```{r, echo = FALSE, message = FALSE}
knitr::read_chunk("similarity_plots.R")
```

```{r setupSimilarity, echo = FALSE, cache = TRUE}
```

```{r similarityHist, echo = FALSE, cache = TRUE}
```

## Peter Slide 2
```{r similarityBar, echo = FALSE, cache = TRUE}
```

## Peter Slide 3
```{r followPlot, echo = FALSE, cache = TRUE}
```
